% Tim Dennis' Resume
% Created: 14 Jan 2012
% Last Modified: 14 Jul 2012

\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

\pagestyle{plain} %was empty
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\input{sections/contact-info}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{phv}\selectfont\Huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

\newenvironment{restabsect}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}
	\begin{tabbing}
	\vspace{3pt}
}{
	\end{tabbing}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape \addr \hfill \phone; \email}

\vspace{8 pt}

\thispagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Experience}
	\begin{ressubsec}{UC San Diego Library}{La Jolla, CA}{Data Services and Collections Librarain (April, 2015 - present)}
		\ressubitem{Provide consultation and training on data discovery and re-use, research data management, and statistical programming to students, faculty and staff.}
		\ressubitem{Serve as UCSD Official Representative to ICPSR.}
		\ressubitem{Administrator of local Dataverse instance.}
		\ressubitem{Instruction}
	\end{ressubsec}

	\begin{ressubsec}{UC Berkeley Library Data Lab}{Berkeley, CA}{Research Technology and Services Specialist (August, 2006- March 2015)}
   		\ressubitem{Build numerous Drupal sites implementing diverse domain requirements with best-practice approaches using behavioral driven development (Gherkin, Behat, Mink).}
		\ressubitem{Write Python scripts for data acquisition, manipulation, and storage.}
		\ressubitem{Provide numeric data/statistical information consultation to students and faculty.}
		\ressubitem{Part of core team to open Library Data Lab in 2007.}
	\end{ressubsec}

	\begin{ressubsec}{UC Berkeley Library}{Berkeley, CA}{Web, Electronic, and Government/Numeric Data Specialist (May, 2002 - August, 2006)}
		\ressubitem{Selected, installed, maintained, \& customized web collaboration applications including wikis, blogs, \& messaging.}
		\ressubitem{Administered library development server including creating and managing accounts, monitoring logs, updating applications, and monitoring usage and security logs.}
		\ressubitem{Managed multiple cross-functional teams in developing and implementing new library web based services.}
		\ressubitem{Trained users and created instruction materials on adoption of new collaboration tools.}
		\ressubitem{Provided numeric data/government information reference to students and faculty via IM, email \& face-to-face.}		
	\end{ressubsec}
	
	\begin{ressubsec}{Information \& Service Design (formerly Center for Document Engineering)}{Berkeley, CA}{Usability Specialist/Researcher (September, 2005 - May, 2006)}
	  \ressubitem{Completed needs assessment, usability analysis and user testing for academic web pattern library application.}
	  \ressubitem{Developed a pattern library using participatory design techniques, personas, scenarios, lo-fi and hi-fi prototyping.}
	  \ressubitem{Developed a web pattern application using parallel development environments in JSP, XSL, XML, \& BerkeleyDB XML and PHP, CSS, XHTML, MYSQL, \& JavaScript.}
	\end{ressubsec}
\end{ressection}

\begin{ressection}{Computing Skills}

	\resitem{Experience in Bash, CSS, Drupal, Excel, Git, HTML, PHP, Python, R, SAS, SPSS, Stata, SQL, Vim, XML}	

\end{ressection}

\input{sections/education}
\input{sections/workshops}
\input{sections/presentations}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{University Service}
	\ressubitem{Research Data Curation Program Team}
	\ressubitem{2013 Research and Academic Engagement Benchmarking Project}

\end{ressection}

\begin{ressection}{Memberships}
	\resitem{International Association for Social Science Information Services and Technology}
	\resitem{Software Carpentry Foundation}
	\resitem{Research Data Alliance}
\end{ressection}

\end{document}
