%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Coordinator of Research Services \\
GW Libraries\\
2130 H Street, NW\\
Washington, DC 20052 }

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Tim Dennis \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
468 41ST Street Apt. B \\ Oakland, CA  94609 \\ (510) 282-4204 % Your address and phone number
\end{center}
\vfill

\signature{Tim Dennis} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Coordinator of Research Services,}

I am interested in applying for the Director of the UCLA Libraries Social Science Data Archive at UCLA Library that was posted on IASST-L mail-list. Given my related experiences and technical capabilities, I hope you consider my application for this job. I believe my experience and skills are a great match for this position.

I started work at UC Berkeley Library as a government documents technical processor working with the government information collections. I was soon providing government information reference and, subsequently, developed an intimate knowledge of government produced statistical products and the major agency surveys. Recognizing the need to enhance my technology skills to support an increasingly digital government document collection, I attended the UC Berkeley School of Information and focused on XML technologies (including standards) and user experience research.

After finishing my masters, I came back to the library and helped plan and open the Data Lab in 2008. I worked hard on developing expertise in data analysis and statistical programming by taking courses on statistics, data science, and software development. I currently provide 15 hours a week of consultation coverage in the Data Lab helping patrons with a range of research data support, including research design, statistical tool instruction, data discovery, understanding, management, and analysis. We typically serve over a thousand users a year, providing in-depth consultation to approximately two-thirds of those users. As my skills have evolved, I can help users in more diverse technical activities, including writing Python or R scripts to scrape data or analyze text.

In addition to working with individual researchers, we regularly work with faculty in the social sciences to integrate the services of the Data Lab with specific course educational outcomes. This can take the form of providing assistance to students working through a statistical problem set or formal instructional workshops on data literacy and data analysis. Although I do not formally select data for the library, I work closely with researchers to identify data files necessary for their research and facilitate the acquisition of these files with various selectors in the library. I feel confident that my knowledge of data sources will make the transition to being a selector relatively seamless.

Along with data and technical aptitudes, I bring a deep understanding of a large research university especially with respect to scholarly communications in the social sciences. I am actively engaged with campus partners on research IT, API development, and articulating needs for data science skills on campus. More recently, I contributed to the Research and Academic Engagement (RAE) Portfolio Planning project, co­authoring a report on Data Analysis Tools. RAE brought together key members from IST, ETS and the Library to benchmark IT service areas against our academic peers, identifying actionable opportunities for improvement. Internally, I am a recognized Drupal expert and provide consultation to our Lirary Systems Office on web development best practices. As a member of International Association for the Social Science Information Services \& Technology (IASSIST), I co-taught a half-day workshop on R and reproducible research last spring in Cologne, Germany. I am also actively engaged with R, Python, and Drupal meetups in the bay area.

I look forward to talking to you more about my experiences and how they map to the desired skills and capabilities expressed in the Data Services Librarian position at GW Libraries.

\closing{Sincerely yours,}


\encl{Curriculum vitae} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
